Index measures for oak decline severity using phenotypic descriptors

### 2020-07-24 manuscript/manuscript.Rmd
added pdi citation

The phenotypic descriptors were analysed using 100 repetitions of unsupervised random forest.
The proximity matrices from each repetition were averaged to a single proximity matrix ($P$).
This was then transformed to a dissimilarity matrix ($1 - P$) and scaled to two dimensions using  multidimensional scaling (MDS).
The first MDS dimension ($D_1$) was inverted ($1 - D_1$) to ensure the correct dimensional orientation relative to decline severity.
It was then min-max scaled to give a scale between 0 and 1 with more severely declining trees having a score closer to 1.
This dimension was named the Phenotypic Decline Index, PDI.
The second MDS dimension ($D_2$) was min-max scaled and then transformed ($2D_2 - 1$) to give a scale between -1 and 1 with COD trees having a score closer to -1 and AOD having a score closer to 1. 
This dimension was named the Decline Acuteness Index, DAI.
The code used to generate the decline indexes is available as an R package pdi version `r packageVersion('pdi') %>% as.character()`, available at https://github.com/jasenfinch/pdi.

>>>>

The phenotypic descriptors were analysed using 100 repetitions of unsupervised random forest.
The proximity matrices from each repetition were averaged to a single proximity matrix ($P$).
This was then transformed to a dissimilarity matrix ($1 - P$) and scaled to two dimensions using  multidimensional scaling (MDS).
The first MDS dimension ($D_1$) was inverted ($1 - D_1$) to ensure the correct dimensional orientation relative to decline severity.
It was then min-max scaled to give a scale between 0 and 1 with more severely declining trees having a score closer to 1.
This dimension was named the Phenotypic Decline Index, PDI.
The second MDS dimension ($D_2$) was min-max scaled and then transformed ($2D_2 - 1$) to give a scale between -1 and 1 with COD trees having a score closer to -1 and AOD having a score closer to 1. 
This dimension was named the Decline Acuteness Index, DAI.
The code used to generate the decline indexes is available as an R package pdi version `r packageVersion('pdi') %>% as.character()` [@finch2020].
